---
title: "FARS package"
author: "Simon Davenport"
date: "2020-06-03"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package was generated an example of an R package for a "Building R packages" 
course.

FARS is a nationwide census providing NHTSA, Congress and the American public 
yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

The FARS package wraps the FARS dataset for the years 2013-2015 and provides some
basic functionality to generate geographical maps plotting the locations of 
accidents per year and US state.

Below is a brief summary of amount of available functionality of the package, 
first a summary of all available datasets, followed by an example of how to make 
a plot

```{r setup}
library(FarsPackage)
```

2013 Dataset

```{r} 
fars_summarize_years(list(2013))
```

2014 Dataset

```{r} 
fars_summarize_years(list(2013))
```

2015 Dataset

```{r} 
fars_summarize_years(list(2013))
```

Plot example, showing accident data for 2014 for Alabama (the 1st state alphabetically)

```{r} 
fars_map_state(1, 2014)
```


